---
title: "Lab2"
author: "Wil Hillmer"
date: "9/14/2020"
output: html_document
```{r}
choco <- read.csv("https://raw.githubusercontent.com/xdaiISU/ds202materials/master/hwlabs/data/choco.csv") 
str(choco)
Rate <- (choco$Rating)
hist(Rate)
boxplot(Rate)
#most of the ratings lie between 2.75 and 3.75 with an average of 3.25. The outliers are around 1.0 and 2.0. 4.0 is not concidered an outlier. 
```{r}
Year <- (choco$Date)
barplot(table(choco$Date), main = "Year and Ratings")
Cocoa <- (choco$Cocoa_Percent)
qqnorm(choco$Rating)
qqline(choco$Rating)
qqnorm(choco$Cocoa_Percent)
qqline(choco$Cocoa_Percent)
library(ggplot2)
test_results <- data.frame(
  score = c(choco$Rating, choco$Cocoa_Percent),
  Test = c(
    rep("Rate", length(choco$Rating)),
    rep("Cocoa", length(choco$Cocoa_Percent))
  )
)
ggplot(test_results, aes(x = Test, y= score, color = Test)) +
geom_boxplot() +
geom_jitter() +
scale_color_brewer(type = "qual", palette = 2) +
theme_minimal() +
theme(legend.position = "none")
delta_0 <- 0

sigma_sq_1 <- 3
sigma_sq_2 <- 2

n_1 <- length(choco$Rating)
n_2 <- length(choco$Cocoa_Percent)

z_stat <- (mean(choco$Rating) - mean(choco$Cocoa_Percent) - delta_0) / 
  sqrt(sigma_sq_1 / n_1 + sigma_sq_2 / n_2)

z_stat
boxplot(choco$Cocoa_Percent)
boxplot(choco$Rating)
#With such a high Z_score we can Reject the null hypthosis of Rate=Cocoa. This means that that the ratings do not depend on the Cocoa Percentage.
boxplot(choco$Cocoa_Percent)
boxplot(Rate)
```{r}
Car1 <- (choco$Characteristics1)
Car2 <- (choco$Characteristics2)
Car3 <- (choco$Characteristics3)
Car4 <- (choco$Characteristics4)
barplot(table(Car1))
barplot(table(Car2))
barplot(table(Car3))
barplot(table(Car4))
#The perfered characteristics of the chocolates would be; Choco, mint, powdery,pure, dirt,sweet, candy, and salt .
```{r}
# For our two analysis we are going to test the rating compaired to the Location and the rating comapired to the Comapny that produced the chocholate.
create <- function(BO){
  barplot(table(choco[!is.na(Rate) & choco$Bean_Origin == BO, "Bean_Origin"], choco[!is.na(Rate) & choco$Bean_Origin == BO, "Rating"] ), main = BO)
  print(summary(choco[!is.na(Rate) & choco$Bean_Origin == BO, "Rating"]))
}

create("Colombia")
create("U.S.A.")
create("Ghana")
create("Peru")
create("Vietnam")
#Based on our results we can determine that All five countries selected produce chocolate with fairly high ratings. The median for all countries was 3.25 which is Classed as Recomended.

